\subsubsection{Project analysis}

\TODO{
    Describe the results that we got from project analysis.
    Say how those compare to already existing results.
    Distribution of code smells that are not yet published.
    How many projects in corpus versus how many were actually successfully analyzed.
    Statistics on code smell distributions inside analyzed applications.
}

As a result, we were able to analyze $X$ applications.
This number is vastly different from the total amount of applications that are present in the corpus for multiple reasons.
Firstly, some of the projects were not using a build system (Gradle or Maven).
This is an issue because to compile the project we would need to specify the classpath manually and
this is quite difficult to do programmatically.
Moreover, even if we managed to compile the projects, SonarQube is provided as a plugin for the build systems which means
that we would still not be able to run the analysis.
Secondly, some of the projects required extra configuration before building, which is also not possible to do
programmatically because each project is different and requires manual configuration.

\subsubsection{Threshold analysis}

\TODO{
We also performed threshold analysis in order to find most suitable values for certain code smells.
}

\TODO{
During threshold analysis, we decided to exclude anonymous classes.
Why?
Android platform does not support lambdas (until very recent versions),
so in order to implement functionalities that are commonly implemented using lambdas,
they use anonymous classes.
Anonymous classes means that there are no attributes and usually only a single method, so
statistics for some input parameters (such as class attribute and method count) might be skewed due
to anonymous classes.
}

\subsubsection{Code smells distributions}

\TODO{
Currently 2 graphs:
\begin{enumerate}
    \item How many applications contain code smell X?
    \item Distribution of detected code smells
\end{enumerate}
}

\TODO{
We can include both results, before updating the thresholds and after?
}
