\TODO{
    Here describe plugin for SonarQube.
    In introduction we mentioned groups that we think the tool might be used for.
    So here we provide our ideas how each group can be helped with our tool,
    provide screenshots or other artifacts that might help our points.

    Describe how queries are transformed into sonarqube implementation
    Describe how we tested the tool (We have X test cases and code coverage was Y percent etc).

    Also describe the results of developing the bulk analyzer, provide simple
    instructions on how to run this tool, provide output from help command, which
    will show input parameters and basic instruction on how to run.
}

\subsubsection{Implementation}

\TODO{
Describe how queries from Kristiina's paper were transformed into SonarQube implementation.
}

As the code smells described by~\citeauthor{refactoring-fowler} are quite abstract, we needed
a more concrete definitions in order to implement the code smells.
In this paper, code smells are defined as Neo4j queries.
However, SonarQube uses different pattern for code smell detection.

In SonarQube, code smells are detected by applying visitor pattern~\cite{visitor_pattern} on the parsed
AST of Java source code.
So in order to translate Neo4j queries into the definitions that are applicable to SonarQube, we used the following
algorithm that can be seen in~\ref{translation_algorithm}.

Firstly, we needed to determine to context of the rule, such as if the rule should detect methods, classes or variables.
Then, we needed to decide if the rule required could be detected in a single scan of the context.
For example, if we need to decide whether or not the method has $X$ amount of parameters, we need would need to visit
this single method only a single time and we do not need to know anything about other methods.
But in some cases, we need to account for other nodes in the tree.
For example, in \verbatim|Shotgun Surgery| we need to detect method invocations that can be present in other classes.

\begin{algorithm}
    \label{translation_algorithm}
    \caption{Translation Neo4j queries into SonarQube rules}
    \KwIn{Neo4j query}
    \KwResult{Neo4j query translated into SonarQube implementation}
    \SetKwFunction{DetermineContext}{DetermineContext}
    \SetKwFunction{SensorRule}{SensorRule}
    \SetKwFunction{RegularRule}{RegularRule}
    \SetKwData{Context}{context}
    \SetKwData{q}{q}
    \SetKwData{r}{r}
    \BlankLine

    \lForEach{Neo4j query \q}{
        \Context$\leftarrow$ \DetermineContext{$q$}
        \uIf{rule \r requires context of other rules}{
            \SensorRule{\Context, \r}
        }
        \Else{
            \RegularRule{\Context, \r}
        }
    }
\end{algorithm}

\subsubsection{Testing}

\TODO{
Here describe that we did unit testing for each rule, and in the end achieved line coverage of 97\%
}

\TODO{
Run the tests to see how many test cases we have.
}

As mentioned in~\ref{subsec:testing}, we also performed internal testing before applying tool to the real projects.
We performed unit testing using \verbatim|Scalatest|~\cite{scalatest}.
In order to measure line coverage, we used \verbatim|codecov|~\cite{codecov} which allowed us to measure
code coverage during every build in the continuous integration (CI) environment.

In the end, we had at least a single positive test case (a code pattern where our analyzer should detect a code smell)
for every rule that we have implemented and we achieved line coverage of $97.25\%$ with $X$ test cases.

\subsubsection{Use cases}

\TODO{
In this section, we should describe how external users can use our tool.
We can focus on 3 groups that we will introduce in introduction.
Developers, project managers and data scientist?
For each group, we can write a section and describe how they can use the tool and see useful
information about the projects.
}

\paragraph{Developers}

\TODO{
    Think of how this tool is useful for developers.
    Obviously this is the main focus group.
}

\TODO{
Developers can use this tool for statical analysis of the application they develop.
Here we can show detailed view of a single code smell, with message line
and rule description and "ideas" on how to fix the bug in the rule description.
}

\paragraph{Project managers}

\TODO{
Project managers can see the overview of the project and how
much code smells there are in the project.
Also they can see how many of each rule, etc.
Here we can show general view of the project (the dashboard).
}

\paragraph{Data scientists}

\TODO{
How can the data scientists use this?
In general, they can export datasets from SonarQube like we did.
Perhaps we can describe here how we did this, and what we managed to create (e.g. analysis results).
With this, they can perhaps find correlations if different code smells can be usually found together.
}
