\subsection{Encountered problems}\label{subsec:encountered-problems}

Previously we also mentioned that plugins are loaded into the SonarQube dynamically and that
this plugin must be used with \verb|provided| scope when compiling the plugin.
This means that only some of the packages are provided during the runtime and not all of the classes
provided by the Sonar Java plugin can be used during the runtime.
This is an issue, because the plugin itself provides a lot of utilities that could be reused inside
the custom rules (for example cognitive complexity counter, lines of code counter).
To overcome this limitation, we extracted those utilities into a separate package and included it in
the compiled artifact of our plugin, so that we could use those tools during the analysis execution.

\subsubsection{Potential usages}

\TODO{
    In this section, we should describe how external users can use our tool.
    We can focus on 3 groups that we will introduce in introduction.
    Developers, project managers and data scientist?
    For each group, we can write a section and describe how they can use the tool and see useful
    information about the projects.
}

\paragraph{Developers}

\TODO{
    Think of how this tool is useful for developers.
    Obviously this is the main focus group.
}

\TODO{
    Developers can use this tool for statical analysis of the application they develop.
    Here we can show detailed view of a single code smell, with message line
    and rule description and "ideas" on how to fix the bug in the rule description.
}

\paragraph{Project managers}

\TODO{
    Project managers can see the overview of the project and how
    much code smells there are in the project.
    Also they can see how many of each rule, etc.
    Here we can show general view of the project (the dashboard).
}

\paragraph{Data scientists}

\TODO{
    How can the data scientists use this?
    In general, they can export datasets from SonarQube like we did.
    Perhaps we can describe here how we did this, and what we managed to create (e.g. analysis results).
    With this, they can perhaps find correlations if different code smells can be usually found together.
}
